### 2020-06-03 7_conclusion.tex
edit figures and indent to bring the paper back to 11 pages

\begin{itemize}

@@

\item While some systems support task granularities as small as 390~ns, this applies only to trivial dependencies and small CPU-based clusters. A number of factors (non-trivial dependencies, accelerators and cluster sizes in the hundreds of nodes) raise the
  METG that any system can reliably achieve by over an order of magnitude: 100~\textmu{}s is a reasonable bound for most applications running at scale with current technologies.

>>>>

\begin{itemize}[leftmargin=*]

@@

\item While some systems support METG(50\%) as small as 390~ns, this applies only to trivial dependencies and small CPU-based clusters. A number of factors (nontrivial dependencies, accelerators and cluster sizes in the hundreds of nodes) raise
  the METGs that can be achieved by over an order of magnitude: 100~\textmu{}s is a reasonable bound for most applications running at scale with current technologies.
